### 2016-10-25 sec-results.tex
Add cross-course comparison of two states; section on varying K.

% highlight interesting latent states discovered; make arguments that
% motivate why it's useful to have a Markov model as the latent state
% representation (capturing transitions between actions is useful and
% more meaningful than just using a discrete distribution as the latent
% state representation); show how the learned state representations differ
% between the two MOOCs

\subsection{Varying the Number of Latent States}
% show what happens as we vary k (particularly interesting to see 2 -> 3
% hidden state change, as the forum "topic" appears suddenly); argue that
% this allows the model to capture behavior patterns at different levels of
% granularity

>>>>

\begin{figure*}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/text-6state/state4.png}
    \caption{A state from \textretrieval{}.}
  \end{subfigure}%
  \begin{subfigure}[t]{0.5\textwidth}
    \includegraphics[width=\textwidth]{figures/sustain-6state/state4.png}
    \caption{A state from \sustain{}.}
  \end{subfigure}
  \caption{Two similar example states found by the 6-state TL-HMM.}
  \label{fig:cross-course}
\end{figure*}

We can also use our model for cross-course behavior analysis. In
Figure~\ref{fig:cross-course} we show two latent state representations
learned by a 6-state TL-HMM, one from \textretrieval{} and one from
\sustain{}. These two states were chosen as they are the most similar
across the two courses. However, if we look at the transitions we can see
some important differences. First, in the state from \textretrieval{}, we
can see that the probability of returning to the course wiki after viewing
a lecture is considerably lower than that probability in the state from
\sustain{}. We also notice that the self-loop for staying in a lecture
activity in \textretrieval{} is significantly higher probability than it is
in the state from \sustain{}. This gives us some insight into the lecture
viewing behavior of students in these two MOOCs which can possibly be a
reflection of the course's structure. In \textretrieval{}, students are
likely to view lecture videos in succession directly without first visiting
the course wiki, whereas in \sustain{} students are much more likely to
first return the course wiki before watching the next lecture video. This
observation would be lost if we did not consider the transitions between
the actions within the latent states.

\subsection{Varying the Number of Latent States}
Our TL-HMM model has a parameter $K$ that sets the number of latent states
to be learned. We believe that this can allow our model to flexibly
discover patterns of different granularity, and we can show this by varying
$K$ for a particular course and observing how the latent state
representations evolve.

\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 1} & \textbf{State 2} & \textbf{State 3} & \textbf{State
    4}\\\hline
    \includegraphics[width=0.22\textwidth]{figures/text-2state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-2state/state1.png}\\
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-3state/state2.png}\\
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state2.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/text-4state/state3.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\textretrieval{} MOOC.} % I don't know why \protect is needed
  \label{fig:text-state-evolution}
\end{figure*}

In Figure~\ref{fig:text-state-evolution} we see the evolution of the latent
state representations found for the \textretrieval{} MOOC\footnote{Due to
space constraints, the graphs are quite small, but the states are in the
same positions as they were in previous figures to aid interpretation.}.
With $K=2$ we uncover a video watching pattern (state 2) and a course
material browsing pattern (state 1). However, we can see that when $K=3$ we
are able to uncover a new pattern involving forum behavior in state 3
(notice the node sizes on the bottom right). As we increase $K$ to four, we
can see that state 2 splits into state 2 and state 4. These states appear
quite similar at a glance, but there are still some key differences. First,
we can see that state 2 now has a non-negligible forum component, whereas
state 4 has hardly any weight on the forum.

\begin{figure*}
  \centering
  \begin{tabular}{cccc}
    \textbf{State 1} & \textbf{State 2} & \textbf{State 3} & \textbf{State
    4}\\\hline
    \includegraphics[width=0.22\textwidth]{figures/sustain-2state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-2state/state1.png}\\
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-3state/state2.png}\\
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state0.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state1.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state2.png}
    &
    \includegraphics[width=0.22\textwidth]{figures/sustain-4state/state3.png}
  \end{tabular}
  \caption{The evolution of states for increasing $K$ for the
  \protect\sustain{} MOOC.} % I don't know why \protect is needed
  \label{fig:sustain-state-evolution}
\end{figure*}

We observe similar behavior in Figure~\ref{fig:sustain-state-evolution}
as we increase $K$ when fitting our TL-HMM on the \sustain{} MOOC. Again,
in the transition between $K=2$ and $K=3$ we discover forum behavior
patterns as a latent state. However, in the transition between $K=3$ to
$K=4$ we instead see a refining of that discovered forum state, where
state 3 captures asymmetric transition probabilities between ``forum thread
view'' and ``forum thread list''. These states could be seen as redundant,
in which case a more appropriate setting of $K=3$ may be appropriate for
the \sustain{} dataset.
